API design for machine learning software: experiences from the scikit-learn project

### 2013-10-18 paper.tex
Use smaller font size for too large snippet.
Another solution is manual line breaking, see:
http://tex.stackexchange.com/questions/10239/breaking-long-lines-using-latex-with-minted-and-pygments
Copyedit intro.

\sklearn is a machine learning library for the Python language.\footnote{\url{http://scikit-learn.org}}
It is designed to be simple and efficient, accessible to
non-experts, and reusable in various contexts. In this article, we present and
discuss the uniform application programming interface shared
by all learning and processing units in the library,
and the way it facilitates composition and reusability. We also comment on
implementation details specific to the Python ecosystem
and analyze potential obstacles faced by users and developers of the library.

@@

The \sklearn project provides a comprehensive suite of machine learning tools,
packaged as a Python library.
It extends this general-purpose language with machine learning operations:
learning algorithms, preprocessing tools, model selection procedures
and a composition mechanism to produce complex ML workflows.
The ambition of the project is to provide efficient implementations
of well-established algorithms within a
programming environment that is accessible to non-experts and
reusable in various scientific areas.
The library is distributed under the simplified BSD license
to encourage its use in both academia and industry.

\sklearn is designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries
\citep{oliphant2007python, vanderwalt2011}.
NumPy augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy extends it further with common numerical operations,
either by implementing these in Python/NumPy
or by wrapping existing C/C{}\verb!++!/Fortran code.
The name ``scikit'' derives from ``SciPy toolkit''
and is shared with \textit{scikit-image}.\footnote{\url{http://scikit-image.org}}
IPython \citep{perez2007ipython} and Matplotlib \citep{hunter2007matplotlib}
complement SciPy to provide a \textsc{matlab}-esque working environment
suited for scientific use.

Since 2007, \sklearn has been developed by more than a dozen
core developers, mostly researchers in various fields
(a.o.\ computer science, neuroscience, astrophysics). It also benefits
from occasional contributors proposing small bugfixes or
improvements. Development proceeds on GitHub\footnote{\url{https://github.com/scikit-learn}},
a platform which greatly facilitates this kind of
collaboration. Because of the large number of developers, emphasis is
put on keeping the project maintainable. In particular, code must follow
specific quality guidelines, such as style consistency and unit-test coverage.
Documentation and examples are required for all features,
and major changes must pass code review by at least two
developers not involved in the implementation of the proposed change.

@@

Since it is common to modify or filter data before feeding it to a learning
algorithm, some estimators in the library implement a \textit{transformer}
interface which defines a \texttt{transform} method. It takes as input some new
data \texttt{X\_test} and yields as output a transformed version of
\texttt{X\_test}. Preprocessing, feature selection, feature extraction and dimensionality reduction
algorithms are all provided as transformers.  In our example,
to standardize the input \texttt{X\_train} to zero mean and unit variance
before fitting the LR estimator, one would write:
\begin{pythoncode}
from sklearn.preprocessing import StandardScaler
scaler = StandardScaler()
scaler.fit(X_train)
X_train = scaler.transform(X_train)
\end{pythoncode}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}. Since a \texttt{StandardScaler} estimator stores the
mean and standard deviation that it computed for the training set, transforming
an unseen test set \texttt{X\_test} maps it into the appropriate region of
feature space:
\begin{pythoncode}
X_test = scaler.transform(X_test)
\end{pythoncode}
Transformers also include a variety of learning algorithms, such as
dimensionality reduction (PCA, manifold learning), kernel approximation,
and other mappings from one feature space to another.

>>>>

{\bf Abstract}
\sklearn is a machine learning library for the Python language.\footnote{\url{http://scikit-learn.org}}
It is designed to be simple and efficient, accessible to
non-experts, and reusable in various contexts. In this article, we present and
discuss the uniform application programming interface shared
by all learning and processing units in the library,
and the way it facilitates composition and reusability. We also comment on
implementation details specific to the Python ecosystem
and analyze potential obstacles faced by users and developers of the library.

@@

The \sklearn library provides a comprehensive suite of machine learning tools
for Python.
It extends this general-purpose programming language with machine learning
operations: learning algorithms, preprocessing tools, model selection procedures
and a composition mechanism to produce complex ML workflows.
The ambition of the library is to provide efficient implementations
of well-established algorithms within a
programming environment that is accessible to non-experts and
reusable in various scientific areas.
The library is distributed under the simplified BSD license
to encourage its use in both academia and industry.

\sklearn is designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries
\citep{oliphant2007python, vanderwalt2011}.
NumPy augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy extends it further with common numerical operations,
either by implementing these in Python/NumPy
or by wrapping existing C/C{}\verb!++!/Fortran code.
The name ``scikit'' derives from ``SciPy toolkit''
and is shared with \textit{scikit-image}.\footnote{\url{http://scikit-image.org}}
IPython \citep{perez2007ipython} and Matplotlib \citep{hunter2007matplotlib}
complement SciPy to provide a \textsc{matlab}-like working environment
suited for scientific use.

Since 2007, \sklearn has been developed by more than a dozen
core developers, mostly researchers in various fields
(among others, computer science, neuroscience, astrophysics). It also benefits
from occasional contributors proposing small bugfixes or
improvements. Development proceeds on GitHub\footnote{\url{https://github.com/scikit-learn}},
a platform which greatly facilitates this kind of
collaboration. Because of the large number of developers, emphasis is
put on keeping the project maintainable. In particular, code must follow
specific quality guidelines, such as style consistency and unit-test coverage.
Documentation and examples are required for all features,
and major changes must pass code review by at least two other
developers.

@@

Since it is common to modify or filter data before feeding it to a learning
algorithm, some estimators in the library implement a \textit{transformer}
interface which defines a \texttt{transform} method. It takes as input some new
data \texttt{X\_test} and yields as output a transformed version of
\texttt{X\_test}. Preprocessing, feature selection, feature extraction and dimensionality reduction
algorithms are all provided as transformers.  In our example,
to standardize the input \texttt{X\_train} to zero mean and unit variance
before fitting the LR estimator, one would write:
\begin{small}
\begin{pythoncode}
from sklearn.preprocessing import StandardScaler
scaler = StandardScaler()
scaler.fit(X_train)
X_train = scaler.transform(X_train)
\end{pythoncode}
\end{small}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}. Since a \texttt{StandardScaler} estimator stores the
mean and standard deviation that it computed for the training set, transforming
an unseen test set \texttt{X\_test} maps it into the appropriate region of
feature space:
\begin{pythoncode}
X_test = scaler.transform(X_test)
\end{pythoncode}
Transformers also include a variety of learning algorithms, such as
dimensionality reduction (PCA, manifold learning), kernel approximation,
and other mappings from one feature space to another.
